30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex
TOR -> Tor

	The most widely used anonymous communication system is TOR. In this paper we will analyze TOR and its semi centralized nature. Furthermore we will look at attempts that have been made to decentralize TOR as well as several other decentralized systems.

>>>>

	The most widely used anonymous communication system is Tor. In this paper we will analyze Tor and its semi centralized nature. Furthermore we will look at attempts that have been made to decentralize Tor as well as several other decentralized systems.
